Exploring Conformational Dynamics and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation

### 2013-08-14 writedown/npt-neq/alanine.tex

\title{Exploring Molecular Conformations and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation}
% \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
\author{Han Wang}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\affiliation{Zuse Institute Berlin, Germany}
\author{Giovanni Ciccotti}
\affiliation{Department of Physics, University of Roma "La Sapienza", Italy}
\author{Luigi Delle Site}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}

@@

Since we are mainly interested in the
nonthermal~\cite{delaHoz2005microwaves} effect of the electric field
to the configuration of a solvated alanine dipeptide, we assume the
alanine is embeded into an infinitely large solvent environment, and
the electric field is only applied to the neighborhood of the alanine.
Any extra heat generated by the electric field can be effectively
absorbed by the solvent environment.  It is argued that such an
accurate reaction temperature control is essential for being able to
perform reproducible experiments~\cite{damm2012can}.
Now the question comes to how to truncate the solvent environment
so that the system can be handled by the limited computer resource.
% In practice, it is impossible to simulate an infinitely large
% environment.
For an equilibrium simulation, the solution is to couple
the system to a thermostat, under which the canonical ensemble can be
sampled by only simulating a finite size system with periodic boundary
condition. For a nonequilibrium simulation, simply couple the system
to a thermostat may not be a good idea, because the \emph{dynamics}
generated by the thermostat is artificial, and deviation from the
Hamiltonian dynamics under investigation will introduce artificial
effects in the nonequilibrium observations. To solve this problem, we
observe that only preserving the Hamiltonian dynamics of the alanine 
itself and the water molecules in the nearby solvation shell is
crucial to the interested nonequilibrium observable
(in this work, it is the conformational change of alanine),
while the detailed dynamics of
the water molecules far away is of less importance. 
Therefore, instead of simulating an infinitely
large system, we only simulate a finite size system with periodic
boundary condition. The simulating region is divided into two
subregions: Near the alanine dipeptide, the dynamics is kept to be
Hamiltonian, and this subregion is called \emph{the Hamiltonian dynamics
region}. While far from the alanine, the dynamics of water is coupled
to a Langevin thermostat, and this region is called \emph{the thermostating
region} (see Fig.~\ref{fig:tmp2}).  For simplicity, the Hamiltonian
dynamics region is assumed to be spherical, centered at the
alpha-carbon of the alanine, and with radius of $R_{ex}$.  Further, we
freeze the movement of the alpha-carbon, so that the alanine is always
located at the center of the simulation region.  The validity of this
setting will be later check by numerical examples showing that the
nonequilibrium observables do not depends on the size of the system
and the size of the Hamiltonian dynamics subregion, if they are
reasonably large and the finite size effect does not play a dominating role.

@@

In this section,
we want to study the nonequilibrium properties of an alanine dipeptide
under a constant EF. At time $t=0$~ps, the system
has been fully equilibriated without any electric field. From $t=0$ to
$t=t_{\textrm{init}}$, the eclectic field is switched on linearly, while
after $t=t_{\textrm{init}}$, the field is kept constant at
$E_{\infty}$.  In this work we consider $t_{\textrm{init}} = 10$~ps,
and $E_{\infty} = 1$~V/nm.
The direction of this field is arbitrarily chosen: along the
$x$ direction. Since the dipole of the equilibrium configurations of
alanine can be along any direction, applying the electric along $x$-axis is
not biased.
The system is set up in a $2.7\times 2.7\times
2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
described by the CHARMM27 force field, and solved in 644 TIP3P
water molecules.
The size of the  Hamiltonian dynamics region is $R_{ex} = 1.0$~nm.
All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
Firstly, an equilibrium NVT simulation of
100~\textsf{ns} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
temperature.  Along the trajectory, configurations were taken every
50~\textsf{ps}, so we use 2000 initial configurations for each nonequilibrium
MD simulation, if not stated otherwise.
% They server as starting point of the branching
% trajectories.
The branching trajectories were integrated by the
Leap-frog scheme with the aforementioned nonequilibrium
temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
``switch'' method provided by Gromacs.  An energy conserving PME
method was applied to calculate the electrostatic interaction in this
periodic system. In the thermostating region, the original dynamics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
The whole system is also coupled to a Parrinello-Rahman barostat with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at the ambient condition (1~Bar). Since the
change of the system size is small and slow, the pressure control
does not have an obviously effect on the
dynamics of the system.

@@

\begin{figure}
  \centering
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-5.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
  \caption{
    The net probability flux and its integration under the constant EF case.
    The warm-up time $t_{init} = 10$~ps.
    The first row shows the probability flux $F_{J,I}(t)$, while the second
    shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (deceasing)
    $Q_{J,I}$ indicates positive (negative) net flux.
    From left to right, the five
    columns present $I = A_1$, $A_2$, $B_1$, $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$. 
    }
  \label{fig:tmp6}
\end{figure}

@@

\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
  % \\
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
  \caption{The
    $x$-component of the dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The dashed line presents the strengths of the
    external electric field, while the solid line presents the dipole
    moments. }
  \label{fig:tmp3}
\end{figure}

The Fig.~\ref{fig:tmp3}
shows that the $x$-component of the dipole moment of the alanine dipeptide
reaches 85\% of the maximum value in only 20~ps, which is comparable to
the warm-up time $t_{init}$. Then the dipole slowly relaxes to the 
maximum value in the following 400~ps. Notice that 20~ps is 25 times
smaller than the slowest time scale of the conformational relaxation.
We calculate the averaged dipole moment of different metastable state
under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
for $A_1$, $A_2$, $B_1$, $B_2$ and $C$, respectively.
Under a constant EF, the system will be driven towards those
conformations that with higher dipole moment, because the
energy of the system will be lowered by aligning the the dipole
to the external EF.
It is clear that
the $\alpha$-helix and left-handed $\alpha$-helix are of higher
dipole moments than $\beta$-sheet conformations, so the probability
of being in the $\alpha$-helix conformations were
observed being increased under the EF.  $A_1$ and $C$ are the most
probable conformations because their dipole moments are the highest
among all metastable conformation. Moreover, the $B_2$  vanishes, because
its dipole is significantly lower than other conformations.
% This also explains the two-time scale behavior of the molecular dipole
% moment.
From 0 to 20~ps, the probability of
lowest dipole conformation $B_2$ quickly
vanishes, so there is a sharp increment of the average molecular
dipole moment. Then until 500~ps, since the conformation slowly migrates from
$B_1$ to $A_1$ and $C$, and also since the dipole moment $A_1$ and $C$
is higher than $B_1$, the average molecular dipole moment slowly increases
to the maximum value.

We also consider the orientation of the alanine dipeptide as a function
of time.
The geometric direction of the alanine is defined by the red vector in
Fig.~\ref{fig:tmp3}, which is the angle bisector of the two black vectors.
The black vectors are define to connect the $\alpha$-carbon and the carbons
on the methyl groups. We define the orientational order parameter
\begin{align}
  S_\theta = \langle 3\sin^2\theta - 2\rangle,
\end{align}
where $\theta$ is the angle between the orientation of the alanine dipeptide
and the direction of the electric field. The order parameter
indicate if the molecule is perpendicular to the electric field.
If the molecule is perfectly perpendicular to the electric field, then $S_\theta = 1$;
If the molecule has no directional
preference at all, then $S_\theta = 0$;
If the molecule is perfectly parallel to the electric field, then $S_\theta = -2$.
From $t=0$ to roughly 10~ps, the orientational order parameter fastly
decreases from 0 to -0.15, which means a weak alignment of the molecule to the external field.
Then from $t=0$ to 500~ps, the molecule slowly changes to the orientation
that is perpendicular to the electric field.

@@

We have tested the periodically oscillating electric field which has
a $\sin$-wave shape:
\begin{align}
  E(t) = E_0\sin(2\pi \omega t),
\end{align}
where $E_0$ is the strength of the field, which is chosen to be
1.0~V/nm.  $\omega$ is the frequency of the field, which is related to
the period $T$ by $\omega = 1/T$.  Here we tested three different
periods: 10, 40 and 200, which corresponding
to frequency 100, 25 and 5~GHz.
% The periods of the later two are
% commensurate to the time scales discovered by the nonequilibrium MD
% simulation of constant electric field. The first is to test the if the
% period is further reduced to smaller than 20~ps, there is any other
% timescale of interest would play a role. Although the periods are
% chosen according to the discovered time scales in the constant
% electric field simulation, the nonequilibrium phenonema of oscillating
% electric field cannot be derived from the constant field system.
% As far as the electric field changes, the internal time scale of the
% system also changes, therefore, the nonequilibrium probabilities is a
% complicated interplay of different internal time scales under
% different EF.
% We do not try to theoretically predict
% what will happen under the oscillating EF by a series constant EF simulation
% revealing the internal dynamics under different strength of EF, but just directly
% do the nonequilibrium MD simulation for the oscillating EF, and discuss
% the observed phenonema.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{fig.ala/graphs/graph-t0010-1.eps}
  \caption{The schematic plot of the main probability flux among the metastable
    states on the Ramachandran histogram
    for periodically oscillating EF, $T=10$~ps. The thickness 
    of the arrows approximately presents the strength of the flux.
  }
  \label{fig:tmp11}
\end{figure}

>>>>

\title{Exploring Conformational Dynamics and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation}
% \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
\author{Han Wang}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\affiliation{Zuse Institute Berlin, Germany}
\author{Giovanni Ciccotti}
\affiliation{Department of Physics, University of Roma "La Sapienza", Italy}
\author{Luigi Delle Site}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}

@@

Since we are mainly interested in the
nonthermal~\cite{delaHoz2005microwaves} effect of the electric field
to the configuration of a solvated alanine dipeptide, we assume the
alanine is embeded into an infinitely large solvent environment, and
the electric field is only applied to the neighborhood of the alanine.
Any extra heat generated by the electric field can be effectively
absorbed by the solvent environment.  It is argued that such an
accurate reaction temperature control is essential for being able to
perform reproducible experiments~\cite{damm2012can}.
Now the question comes to how to truncate the solvent environment
so that the system can be handled by the limited computer resource.
% In practice, it is impossible to simulate an infinitely large
% environment.
For an equilibrium simulation, the solution is to couple
the system to a thermostat, under which the canonical ensemble can be
sampled by only simulating a finite size system with periodic boundary
condition. For a nonequilibrium simulation, simply couple the system
to a thermostat may not be a good idea, because the \emph{dynamics}
generated by the thermostat is artificial, and deviation from the
Hamiltonian dynamics under investigation will introduce artificial
effects in the nonequilibrium observations. To solve this problem, we
observe that only preserving the Hamiltonian dynamics of the alanine 
itself and the water molecules in the nearby solvation shell is
crucial to the interested nonequilibrium observable
(in this work, it is the conformational change of alanine),
while the detailed dynamics of
the water molecules far away is of less importance. 
Therefore, instead of simulating an infinitely
large system, we only simulate a finite size system with periodic
boundary condition. The simulating region is divided into two
subregions: Near the alanine dipeptide, the dynamics is kept to be
Hamiltonian, and this subregion is called \emph{the Hamiltonian dynamics
region}. While far from the alanine, the dynamics of water is coupled
to a Langevin thermostat, and this region is called \emph{the thermostating
region} (see Fig.~\ref{fig:tmp2}).  For simplicity, the Hamiltonian
dynamics region is assumed to be spherical, centered at the
alpha-carbon of the alanine, and with radius of $R_{ex}$.  Further, we
freeze the movement of the alpha-carbon, so that the alanine is always
located at the center of the simulation region.
Therefore, the dynamics is preseved in the Hamiltonian dynamics region (where the properties of interest are observed)
and the artificial effect of thermostating is negligible.
At the same time, the thermostating region works as a infinitely large
environment that effectively absorbs the extra heat, so that
the nonthermal effect can be studied.
The validity of the above
statement will be later check latter by numerical examples showing that the
nonequilibrium observables do not depends on the size of the system
and the size of the Hamiltonian dynamics subregion, if they are
reasonably large and the finite size effect does not play a dominating role.

@@

In this section,
we want to study the nonequilibrium properties of an alanine dipeptide
under a constant EF.  At time $t=0$~ps, the system
has been fully equilibriated without any electric field. From $t=0$ to
$t=t_{\textrm{init}}$, the eclectic field is switched on linearly, while
after $t=t_{\textrm{init}}$, the field is kept constant at
$E_{\infty}$.  In this work we consider $t_{\textrm{init}} = 10$~ps,
and $E_{\infty} = 1$~V/nm.
The direction of this field is arbitrarily chosen: along the
$x$ direction. Since the dipole of the equilibrium configurations of
alanine can be along any direction, applying the electric along $x$-axis is
not biased.
Being more general, in this paper we denote the
electric field as a function of time $\vect E(t)$.
Therefore, the constant electric field is
$\vect E(t) = (E_\infty\cdot t/t_{init},0,0)$ as $0\leq t < t_{init}$, and 
$\vect E(t) = (E_\infty,0,0)$
as $t \geq t_{init}$.
The system is set up in a $2.7\times 2.7\times
2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
described by the CHARMM27 force field, and solved in 644 TIP3P
water molecules.
The electric field exserts force $\vect F = q \vect E(t)$ on
the partial charge $q$ in the system.
The size of the  Hamiltonian dynamics region is $R_{ex} = 1.0$~nm.
All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
Firstly, an equilibrium NVT simulation of
100~\textsf{ns} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
temperature.  Along the trajectory, configurations were taken every
50~\textsf{ps}, so we use 2000 initial configurations for each nonequilibrium
MD simulation, if not stated otherwise.
% They server as starting point of the branching
% trajectories.
The branching trajectories were integrated by the
Leap-frog scheme with the aforementioned nonequilibrium
temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
``switch'' method provided by Gromacs.  An energy conserving PME
method was applied to calculate the electrostatic interaction in this
periodic system. In the thermostating region, the original dynamics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
The whole system is also coupled to a Parrinello-Rahman barostat with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at the ambient condition (1~Bar). Since the
change of the system size is small and slow, the pressure control
does not have an obviously effect on the
dynamics of the system.

@@

\begin{figure}
  \centering
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-5.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
  \caption{
    The net probability flux and its integration under the constant EF case.
    The warm-up time $t_{init} = 10$~ps.
    The first row shows the probability flux $F_{J,I}(t)$ with unit $\textrm{ps}^{-1}$, while the second
    shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (deceasing)
    $Q_{J,I}$ indicates positive (negative) net flux.
    From left to right, the five
    columns present $I = A_1$, $A_2$, $B_1$, $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$. 
    }
  \label{fig:tmp6}
\end{figure}

@@

\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
  % \\
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
  \caption{The
    $x$-component of the dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The dashed line presents the strengths of the
    external electric field, while the solid line presents the dipole
    moments. The left vertical axis is for the dipole moment, while
    the right is for the orientational order parameter.
  }
  \label{fig:tmp3}
\end{figure}

The Fig.~\ref{fig:tmp3}
shows that the $x$-component of the dipole moment of the alanine dipeptide
reaches 85\% of the maximum value in only 20~ps, which is comparable to
the warm-up time $t_{init}$, and is 25 times
smaller than the slowest time scale of the conformational relaxation.
Then in the following 400~ps, the dipole slowly relaxes to the 
maximum value, that reads
6.8~Debye, and is  corresponding to a dipole energy of ca.
$-13.6$~kJ/mol. The main free energy barriers among the
metastable states are reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
which is comparable to the dipole energy. This explains the 
conformational changes under the electric field.
We calculate the averaged dipole moment of different metastable state
under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
for $A_1$, $A_2$, $B_1$, $B_2$ and $C$, respectively.
Under a constant EF, the system will be driven towards those
conformations that with higher dipole moment, because the
energy of the system will be lowered by aligning the the dipole
to the external EF.
It is clear that
the $\alpha$-helix and left-handed $\alpha$-helix are of higher
dipole moments than $\beta$-sheet conformations, so the probability
of being in the $\alpha$-helix conformations were
observed being increased under the EF.  $A_1$ and $C$ are the most
probable conformations because their dipole moments are the highest
among all metastable conformation. Moreover, the $B_2$  vanishes, because
its dipole is significantly lower than other conformations.
% This also explains the two-time scale behavior of the molecular dipole
% moment.
From 0 to 20~ps, the probability of
lowest dipole conformation $B_2$ quickly
vanishes, so there is a sharp increment of the average molecular
dipole moment. Then until 500~ps, since the conformation slowly migrates from
$B_1$ to $A_1$ and $C$, and also since the dipole moment $A_1$ and $C$
is higher than $B_1$, the average molecular dipole moment slowly increases
to the maximum value.

We also consider the orientation of the alanine dipeptide as a function
of time.
The geometric direction of the alanine is defined by the red vector in
Fig.~\ref{fig:tmp3}, which is the angle bisector of the two black vectors.
The black vectors are define to connect the $\alpha$-carbon and the carbons
on the methyl groups. We define the orientational order parameter
\begin{align}
  S_\theta = \langle 3\sin^2\theta - 2\rangle,
\end{align}
where $\theta$ is the angle between the orientation of the alanine dipeptide
and the direction of the electric field. The order parameter
indicate if the molecule is perpendicular to the electric field.
If the molecule is perfectly perpendicular to the electric field, then $S_\theta = 1$;
If the molecule has no directional
preference at all, then $S_\theta = 0$;
If the molecule is perfectly parallel to the electric field, then $S_\theta = -2$.
From $t=0$ to roughly 10~ps, the orientational order parameter fastly
decreases from 0 to $-0.15$, which means a weak alignment of the molecule to the external field.
Then from $t=0$ to 500~ps, the molecule slowly changes to the orientation
that is perpendicular to the electric field.

@@

We have tested the periodically oscillating electric field which has
a $\sin$-wave shape:
\begin{align}
  \vect E(t) = (E_0\sin(2\pi \omega t), 0, 0)
\end{align}
where $E_0$ is the strength of the field, which is chosen to be
1.0~V/nm.  $\omega$ is the frequency of the field, which is related to
the period $T$ by $\omega = 1/T$.  Here we tested three different
periods: 10, 40 and 200, which corresponding
to frequency 100, 25 and 5~GHz.
% The periods of the later two are
% commensurate to the time scales discovered by the nonequilibrium MD
% simulation of constant electric field. The first is to test the if the
% period is further reduced to smaller than 20~ps, there is any other
% timescale of interest would play a role. Although the periods are
% chosen according to the discovered time scales in the constant
% electric field simulation, the nonequilibrium phenonema of oscillating
% electric field cannot be derived from the constant field system.
% As far as the electric field changes, the internal time scale of the
% system also changes, therefore, the nonequilibrium probabilities is a
% complicated interplay of different internal time scales under
% different EF.
% We do not try to theoretically predict
% what will happen under the oscillating EF by a series constant EF simulation
% revealing the internal dynamics under different strength of EF, but just directly
% do the nonequilibrium MD simulation for the oscillating EF, and discuss
% the observed phenonema.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{fig.ala/graphs/graph-t0010-1.eps}
  \caption{The schematic plot of the main probability flux among the metastable
    states on the Ramachandran histogram
    for periodically oscillating EF, $T=10$~ps. The thickness 
    of the arrows approximately presents the strength of the flux.
    The numbers near the arrows indicates the strength of the averged
    probability flux, the unit of which is $10^{-3}\textrm{ps}^{-1}$.
  }
  \label{fig:tmp11}
\end{figure}
